---
title: "Plot Normal distribution exercise"
author: "Birka Jensen"
date: "27. apr. 2016"
output: html_document
---

The point of this exercise is to learn how to plot functions in R and visualize data in R. 
To accomplish this I will write a program that will draw the normal densityfuntion and cdf in one plot each. the first plot will be the normal density with mean = 0, and sd = i for i = 1,2,3...10. the second will be the normal cdf with mean 1 and sd = i. 

The following is the function "distribution.change" that takes n as the number of simulated random variables to base the visualization on.

```{r}
distribution.change = function(n){

i=seq(1,10)
M = sapply(i, function(i) data = rnorm(n,0,i))
M[,1]=sort(M[,1])
plot(0,0, main = paste("PDF of ",n), type= 'l', xlim=c(-25,25), ylim = c(0,0.5))
  for (i in 1:10){
    M[,i]=sort(M[,i])
    lines(M[,i],dnorm(M[,i],0,i),col = rgb((i/10),0,0))
  }
plot(0,0,xlim = c(-25,25),ylim= c(0,1.1),main = paste("CDF of ",n), type = 'l')
  for(i in 1:10){
  lines(ecdf(M[,i]), col = rgb((i/10),0,0))
  }  
}
```

This bit of code first makes a 2 by 2 grid for the plots and then calls distributionchange with n=100, n=1000 and n=10000 respectively. Results can be seen below.

```{r}
par(mfrow=c(3,2),mar=c(2,2,2,2))
distribution.change(100)
distribution.change(1000)
distribution.change(10000)
```

