---
title: "Distribution"
author: "Nguyen"
date: "28. apr. 2016"
output: html_document
---
This function simply generates 10000 normally distributed random variables, with inputs, the mean and standard deviation.
```{r}
distribution.change<-function(m,sd){
n<- 10000
return(rnorm(n,m,sd))
}
```

Below is the code to plot the density of the generated random variables with fixed mean and standard deviation varies from 1 to 10.
```{r}
for(i in 1:10){
  X<-distribution.change(10,i)
  if(i>1){
    lines(density(X),col=rgb(i/10,0,0))     #rbg() can be replace by col=i for colorfulness
    
  }else{
    plot(density(X), col=i, ylab = "Density", xlab = "X",main="Density of the generated normal RV's with SD varies from 1-10")
  }
}

```

 *As observed the higher the deviation the flatter the graph.*
 
Below is the code to plot the CDF of the generated random variables with fixed mean and standard deviation varies from 1 to 10.

```{r}
for(i in 1:10){
  X<-distribution.change(10,i)
  if(i>1){
    lines(ecdf(X),col=rgb(i/10,0,0)) #rbg() can be replace by col=i for colorfulness
  }else{
    plot(ecdf(X), col=rgb(i/10,0,0), ylab = "CDF", xlab = "X",main="CDF of the generated normal RV's with SD varies from 1-10")
  }
}

```
 