---
title: "Exercise 9, Chapter 3"
author: "Thomas B. Jørgensen"
date: "25 april 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Consider the following double integral
\begin{align}
\int_0^\infty\int_0^x e^{-(x+y)}dy\;dx
\end{align}
with the following analytic solution
\begin{align}
\int_0^\infty\int_0^x e^{-(x+y)}dy\;dx&=\int_0^\infty    e^{-x}-e^{-2x}   dx\\
&=\left[  -e^{-x}+\frac{e^{-2x}}{2}  \right]_0^\infty\\
&=\frac{1}{2}
\end{align}
For $y$ observe that its upper limit $f(x)=x$ exactly divides in two the domain $\Omega=[0,\infty]\times [0,\infty]$, thus we can rewrite $(1)$ so as to obtain the following integral
\begin{align}
\int_0^\infty\int_0^x e^{-(x+y)}dy\;dx=\frac{1}{2}\cdot\int_0^\infty\int_0^\infty e^{-(x+y)}dy\;dx
\end{align}
Now, the rhs of $(5)$ is separable i.e. split the integral into two components
\begin{align}
\int_0^\infty e^{-x}dx\cdot\int_0^\infty e^{-y}dy
\end{align}
Define the function $f(z)=e^{-z}$ with $z\in [0,\infty]$ then it's straightforward to generate values of $f(z)$ using random uniform numbers $U=[0,1]$ be means of the following composite function
\begin{align}
g(U)=\frac{f(\frac{1}{U}-1)}{U^2}=\frac{e^{1-\frac{1}{U}}}{U^2}
\end{align}
where we used the substitution $U=\frac{1}{z+1}$.
Obviously we must generate two random uniform numbers $U1,U2$ and then taking the product of applying $(7)$ for $U1$ and $U2$.
The following program implements the idea
```{r cars}
n <- 500000
total <- 0
for (i in 1:n) {
    U1 <- runif(1)
    U2 <- runif(2)
    total <- total+exp(1-1/U1)/((U1)^2)*exp(1-1/U2)/((U2)^2)
}
(1/2)*total/n
```
with values very close to $(4)$.
