---
title: "Exercise Regression 2.2 Using R properly"
author: "Emil H. Andersen"
date: "May 20, 2016"
output: pdf_document
---

The exercise uses information from the data set [indicator.txt](http://www.stat.tamu.edu/~sheather/book/docs/datasets/indicators.txt)

#Task a)

```{r}
data <- read.table("indicators.txt",header=TRUE)
a <- lm(data$PriceChange~data$LoanPaymentsOverdue)
plot(data$LoanPaymentsOverdue,data$PriceChange,ylim=c(-30,15))
abline(a, col="red")
x <- seq(0,10,0.1)
ytop <- 11.5611000 -0.3335853*x
ybot <- -2.532112 -4.163454*x
lines(x,ytop,lty=2)
lines(x,ybot,lty=2)
```

We use information from the summary and confint functions of R.

```{r}
summary(a)
confint(a,level=0.95)
```

We see from the confint function, that the $95 \%$ confidence interval for $\beta_1$ is $[-4.163454,-0.3335853]$. We can say that we are $95 \%$ confident that there is a negative linear association, since this entire interval shows a negative decrease as LoanPaymentsOverdue increases. So this is definitely a negative linear association.

#Task b)

Using information from summary and confint, we get

```{r}
ymean <- 4.5145 -2.2485*4
ybotCI <- -2.532112 - 4.163454*4
ytopCI <- 11.5611000 - 0.3335853*4
c(ymean,ybotCI,ytopCI)
```

We observe from this estimation, that $E(Y|X=x) = -4.47950$, and the $95 \%$ confidence interval is $[-19.18593,10.22676]$.

We can conclude that $0$ is a reasonable answer for $E(Y|X=x)$ because of the large confidence interval, which happens to contain $0$.
