---
title: "Exercise2.11 montecarlo in r"
author: "Maria"
date: "30-04-2016"
output: pdf_document
---
### Exercise 2.11 a
I should generate a binomial $Bin(n, p)$ random variable with $n = 25$ and $p = .2$.
After that I should plot a histogram for a simulated sample and compare it with the binomial mass function.
This is done in the following R-code: 

```{r}
#Exercise 2.11 a

nsim<-5000 #number of random numbers
n=25;p=.2; #parametre to binomial
y=seq(0,n,by=1) #sequence used to generate the binomial
cp=pbinom(y,n,p) #make cdf of binomial
X=rep(0,nsim) # A vector to store in 
for(i in 1:nsim){
  u=runif(1)
  X[i]=sum(cp<u) #checks to see what interval the uniform random variable fell in and
  #assigns the correct Poisson value to X
}
hist(X,freq=F) #histogram
lines(1:n,dbinom(1:n,n,p),lwd=2) #Density function
system.time(rbinom(5000,25,.2))  #Calculate time

# Generate binomial from a function
MYbinom<-function(s0,n0,p0){
  cp=pbinom(seq(0,n0,by=1),n0,p0) #make cdf of binomial
  X=rep(0,s0) #Vector to store 
  for (i in 1:s0){
    u=runif(1)
    X[i]=sum(cp<u) #checks to see what interval the uniform random variable fell in and 
    #assigns the correct Poisson value to X
  }
  return(X)
}
system.time(MYbinom(5000,25,.2)) #calculate time 

```

It is seen that the histogram and line looks ok but not perfect. 
When the time is calculated it can be seen that the first method is better than the other method 

### Exercise 2.11 b
In this exricse there shall be shown that the code below (the function original) produces a random variable U from $U([0,a])$.  
This shall be compared  with the transform $\alpha U$ ,$U \sim U (0, 1)$ for values of $\alpha$ close to 0 and close to 1, and with runif(1,max=alpha).
There is used the following R-code:
```{r}
original<-function(s0,alpha){  #Make function
  U=rep(0,s0) #Vector to store in 
  for (i in 1:s0){
    u=runif(1)
    while (u > alpha) u=runif(1)
    U[i]=u #Takes the u in a vector
  }
    return(U) #Return u
  


}
par(mfrow=c(1,2))
hist(original(1000,.1)) #Make histogram

system.time(original(1000,.1)) #calculate time 

Trans<-function(s0,alpha){ #Funcrtion there made the transoform alpha*u
  U=rep(0,s0) #Vector to store in 
  for (i in 1:s0) {
    U[i]=alpha*runif(1) #The transform alpha*u
}
return(U)
}
hist(Trans(1000,.1)) #Make histogram
system.time(Trans(1000,.1)) #Calculate the time 
```

It can be seen that when $\alpha$ is small when the first program is very slow. 