---
title: "Exercise Regression 2.2"
author: "Emil H. Andersen"
date: "May 18, 2016"
output: pdf_document
---

The exercise uses information from the data set [indicator.txt](http://www.stat.tamu.edu/~sheather/book/docs/datasets/indicators.txt)

#Task a)

```{r}
data <- read.table("indicators.txt",header=TRUE)
data
```

First, we look at the scatterplot of the PriceChange and LoanPaymentsOverdue
You can also embed plots, for example:

```{r, echo=FALSE}
plot(data$LoanPaymentsOverdue,data$PriceChange, xlab="LoanPaymentsOverdue",ylab="PriceChange")
```

We can observe from the scatterplot that it very slightly resembles a negative relation, which is good news, since this is what we want to show!

Now, we fit a linear model based on this data

```{r}
fit <- lm(data$PriceChange~data$LoanPaymentsOverdue)
summary(fit)
```

We can observe from this summary, specifically from the intercept estimate and the "data$LoanPaymentsOverdue" estimates, that the least squares best of fit is defined as: $y = 4.5145 - 2.2485 \cdot x$

```{r}
x <- seq(0,7,0.1)
y <- 4.5145 - 2.2485*x
```

Plotting this on top of the scatter plot results in:

```{r, echo=FALSE}
plot(data$LoanPaymentsOverdue,data$PriceChange, xlab="LoanPaymentsOverdue",ylab="PriceChange")
lines(x,y,col="red")
```

Now, we calculate the residuals, to use to calculate the standard error of $\beta _1$:

```{r}
y2 <- 4.5145 - 2.2485*data$LoanPaymentsOverdue
error <- data$PriceChange - y2
S <- sqrt((1/(length(error)-2))*sum(error^2))
SXX <- sum((data$LoanPaymentsOverdue - mean(data$LoanPaymentsOverdue))^2)
seB <- S/sqrt(SXX)
B1 <- -2.2485
error
seB
```

We can also test the hypothesis $H_0 : \beta_1 = 0$ against $H_A : \beta_1 \neq 0$:

```{r}
Tt <- (-2.2485-1)/seB
Tt
1-pt(Tt,18-2)
```

To get a confidence interval of $95 \%$, the slope of the regression line is given by: $(\hat{\beta_1} - t(\alpha /2,n-2)se(\hat{\beta_1}),\hat{\beta _1} + t(\alpha /2 , n-2)se(\hat{\beta_1}))$ 

$= (-2.2485 - t(0.025,16)0.9033113,-2.2485 + t(0.025 , 16)0.9033113)$

Where t is a t-distribution. We have that:
```{r}
c(-qt(0.975,16)*seB,qt(0.975,16)*seB)
```

So a 95% confidence interval for B1 would be $-2.2485 \pm 1.914934$. As such, we can see that there must be a negative linear relation Price Change and Loan Payments Overdue, even with the very large interval that it has.

#Task b)

We estimate $E(Y|X=4)$ using the fitted regression model from before:

```{r}
y3 <- 4.5145 - 2.2485*4
y3
```

Then we find a $95\%$ confidence interval for $E(Y|X=4)$:
```{r}
c(-qt(0.975,length(error-2))*S*sqrt(1+1/length(error)+
                                      (4-mean(data$LoanPaymentsOverdue))^2/SXX),
  qt(0.975,length(error-2))*S*sqrt(1+1/length(error)+(4-mean(data$LoanPaymentsOverdue))^2/SXX))
```
So we have a confidence interval of $[-13.06022,4.10122]$. Note that $0$ is in fact in the interval, so $0\%$ is a reasonable result for $E(Y|X=4)$.


