---
title: 'Installing from GitHub!'
author: "E. F. Haghish"
date: "20 Apr 2016"
output: html_document
---

In the previous lecture, I was asked to "reinstall" the packages required for 
a particular computation, within **rmarkdown**. I was using the 
`, eval = FALSE` argument which tells R only to print the code-chunk in the 
document without executing it. When we tried to execute the code, we got 
an error from RStudio. I looked in the error today and it seems we have to 
specify the repository of the package. For **CRAN** packages, it would be 
as follows. 

To test this, I install my own `DOT` package from CRAN
```{r}
install.packages("DOT", repos = 'http://cran.us.r-project.org')
```

##### But what if your package is not on CRAN, and it's hosten on GitHub instead?

I looked into that as well. To test this, I'm going to install my `graphConver` 
package from GitHub. To do this we need to make sure we have the 'devtools' library intalled.

```{r}
install.packages("devtools", repos = 'http://cran.us.r-project.org')
library(devtools)
install_github("haghish/convertGraph")
```

I can't wait to see you all on GitHub. 
[Here is my GitHub account](https://github.com/haghish/). I have created a 
repository for the course where I **SHARE** some codes with the class through 
GitHub. Forking is a term for connecting 
to an existing project created by someone else. 

[**You Should Fork This Repository!** ](https://github.com/haghish/ST516)
 




