---
title: "Exercises from Chapter 3"
author: "Nguyen Khanh Le Ho"
date: "21. apr. 2016"
output: html_document
---


**Problem 12**

Let $N=\min\{n:\sum\limits_{i=0}^nU_i>1\}$, where $U_i\sim U(0,1)$ for $i\geq 1$. Thus $N$ is a random number and we want to estimate $E(N)$ by generating 100,1000 and 10000 values of $N$. 


***To Generate $N$***

The idea is to generate one random uniform number $U_i$ at a time and add them together exactly until the sum exceed 1, then we count how many of those have been added.

*Below is the code to generate the random number $N$. The function **RN12**, takes as input the sample size, and returns the sample mean which is an estimation for $E(N)$.*
```{r}
RN12<-function(n){
  N2<-rep(0,n) #storage for the n random numbers.
  for(i in 1:n){

    N=0 # There is no sum in the begining, thus no uniform random number.
    S=0 # The sum is 0 in the begining.
    
    while(S<=1){ # Check wether the sum of the uniform random numbers exceed 1.
      U<-runif(1)
      S=S+U 
      N=N+1
    }

  N2[i]=N # Once the sum exceed 1 store the random number N and repeat the experiment.
  }

return(mean(N2))
}
```

(a) Using a sample of size 100 yields
```{r}
RN12(100)
```
(b) Using a sample of size 1000 yields
```{r}
RN12(1000)
```
(c) Using a sample of size 10000 yields
```{r}
RN12(10000)
```
(d) I think that this is a cool way to estimate $e$. :-)

**Problem 13**

Let $N=\max\{n:\prod\limits_{i=0}^nU_i\geq e^{-3}\}$, where $U_i\sim U(0,1)$ for $i\geq 1$. Thus $N$ is a random number and we want to estimate $E(N)$ by simulation. 

***To Generate $N$***

Similar approach as in problem 12.

*Below is the code for generating the desired random numbers. The function **RN12**, takes as input the sample size, and returns the sample mean which is an estimation for $E(N)$.*

```{r}
RN13<-function(n){
  N2<-rep(0,n)
  
  for(i in 1:n){
    P=1  # The product is 1, when N is 0.
    N=0  # N the number of uniform random number is 0 in the begining.
    
    while(P>exp(-3)){ #Check whether the product exceed e^-3.
      U<-runif(1)
      P=P*U           
      N=N+1           #the number of uniform random number in the product is increased by 1.
    }
    
    N2[i]=N
  }
  
  return(mean(N2))
}
```

(a) Below an estimation for $E(N)$ using a sample of size 10000  
```{r}
RN13(10000)
```
(b) Estimation for $P(N=i)$ for $i=0,...,6$, with sample of size 10000. The idea is to generate 10000 random numbers $N$, then the probability $P(N=i)\approx \frac{\#\{N=i\}}{10000}$, where $\#\{N=i\}$ is the number of the simulated random numbers $N$ that attained value $i$.

```{r}
n<- 10000
N2<-rep(0,n)
for(i in 1:n){
    P=1
    N=0
    while(P>exp(-3)){
      U<-runif(1)
      P=P*U
      N=N+1
    }
    N2[i]=N
}
P0= length(N2[N2==0])/10000
P1= length(N2[N2==1])/10000
P2= length(N2[N2==2])/10000
P3= length(N2[N2==3])/10000
P4= length(N2[N2==4])/10000
P5= length(N2[N2==5])/10000
P6= length(N2[N2==6])/10000
```
 Estimation for $P(N=0)$
```{r}
P0
```
 Estimation for $P(N=1)$
```{r}
P1
```
 Estimation for $P(N=2)$
```{r}
P2
``` 

Estimation for $P(N=3)$

```{r}
P3
```
Estimation for $P(N=4)$
```{r}
P4
```

Estimation for $P(N=5)$
```{r}
P5
```
Estimation for $P(N=6)$

```{r}
P6
```
