---
title: "Chapter_8_Exercise_14"
author: "Birka Jensen"
date: "29. apr. 2016"
output: html_document
---

Exercise 14 chapter 8:
======================

If n = 2 and $X_1=1$ and $X_2=3$, what is the bootstrap estimate of Var($S^2$) (where $S^2$ is the sample variance).

First observe that $P(X_1)=\frac{1}{2}=P(X_2)$

To generate $X_e$ (a random Variable that takes on the value 1 with probability 1/2 and 3 with probability 1/2) do as follows:
```{r}
n=1000
M=sapply(1:100,function(i) runif(n,0,1)) #matrix of 100 columns each containing 1000 U(0,1) R.V.'s
#U=runif(1000,0,1) #generate 1000 U(0,1) R.V.'s
X=c() #initialize vector

RVChoice = function(u){ #function to easily simulate X_i
  if(u<.5){X=append(X,1)
  }
  else{X=append(X,3)
    }
}
XM=apply(M,c(1,2), RVChoice) #a Matrix with 100 columns each containing 1000 simulated X_e, R.V.'s with F_e
plot(ecdf(XM[,1])) #plot the cdf of simulated variable X_i in the first sample of the matrix
```

Now we have a matrix XM that contains 100 samples of size=1000 of the random variable $X_e$ 


```{r}

samplemean=apply(XM,2,function(x) mean(x)) #a vector with the samplemean of each of the columns of XM

samplevariance=c() #initialize a vector "samplevariance"

#using definition of the sample variance from page 137 (Ross),this for loop calculates the sample variance of each of the rows in XM
for(i in 1:100){  
  samplevariance=append(samplevariance,sum(sapply(XM[,i], function(x) (x-samplemean[i])^2))/(n-1))
  } 
```

To obtain an estimate of the variance of the sample variance, I take the variance of the values in the vector containing samplevariances.

```{r}
#the estimated variance of the sample variance
var(samplevariance)  
```

