---
title: "Chapter_8_Exercise_14"
author: "Birka Jensen"
date: "29. apr. 2016"
output: html_document
---

Exercise 14 chapter 8:
======================

If n = 2 and $X_1=1$ and $X_2=3$, what is the bootstrap estimate of Var($S^2$) (where $S^2$ is the sample variance).

First observe that $P(X_1)=\frac{1}{2}=P(X_2)$

To generate $X_e$ (a random Variable that takes on the value 1 with probability 1/2 and 3 with probability 1/2) do as follows:
```{r}
set.seed(1)
n=2
M=sapply(1:1000,function(x) sample(c(1,3),2,replace=TRUE)) #matrix of 1000 columns each containing 2 R.V.'s that is a sample from the empirical distribution



#M  #uncomment if you want to see the matrix of samples
plot(ecdf(c(1,3))) #plot the cdf of simulated variable X_i in the first sample of the matrix
```


Now we have a matrix XM that contains 100 samples of size=1000 of the random variable $X_e$ 
```{r}

samplemean=apply(M,2,function(x) mean(x)) #a vector with the samplemean of each of the columns of XM

samplevariance=c() #initialize a vector "samplevariance"

#using definition of the sample variance from page 137 (Ross),this for loop calculates the sample variance of each of the rows in XM
for(i in 1:100){  
  samplevariance=append(samplevariance,sum(sapply(M[,i], function(x) (x-samplemean[i])^2))/(n-1))
  } 
```

To obtain an estimate of the variance of the sample variance, I take the variance of the values in the vector containing samplevariances.

```{r}
#the estimated variance of the sample variance
var(samplevariance)  
```

